An empirical study of fixation for strategies in the Iterated Prisoner's Dilemma

### 2017-04-26 tex/main.tex
Change a number of styles of plots and writing.
Modified the format from horizontal to vertical and I also used a
correlation matrix (which was essentially what I was doing before).

Figure~\ref{fig:moran_process} shows a diagrammatic representation of the Moran
process. The Moran process is a stochastic birth death process on a finite
population in which the population size stays constant over time. Individuals
are \textbf{selected} according to a given fitness landscape. Once selected, a
given individual is reproduced and similarly another individual is chosen to be
removed from the population. In some settings mutation is also considered but
without mutation (the case considered in this work) this process will arrive at
an absorbing state where the population is entirely made up of a single
individual. The probability with which a given strategy is the survivor is
called the absorption probability. A more detailed analytic description of this
is given in Section~\ref{sec:validation}.

@@

The Moran process was initially introduced in \cite{Moran1957} in a genetic
setting. It has sine been used in a variety of settings including the
understanding of the spread of cooperative behaviour. However, as stated before,
these mainly consider non sophisticated strategies. Some work has looked at
evolutionary stability of strategies within the Prisoner's Dilemma \cite{Li2014}
but this is not done in the more widely used setting of the Moran process but in
terms of infinite population stability. In \cite{Baek2016} Moran processes are
looked at in a theoretic framework for a small subset of strategies. In
\cite{Lee2015} machine learning techniques are used to train a strategy capable
of resisting invasion and also invade any memory one strategy. Recent work
\cite{Hilbe2017} has investigated the effect of memory length on strategy
performance and the emergence of cooperation but this is not done in Moran
process context and only considers specific cases of memory 2 strategies.
% TODO Is this OK? We should add more.

The contribution of this work is a detailed and extensive analysis of absorption
probabilities for 172 strategies. These strategies and the numerical simulations
are from~\cite{axelrodproject} which is an open source research library written
for the study of the IPD\@. The strategies and simulation frameworks are
automatically tested in accordance to best practice. The large number of
strategies are available thanks to the open source nature of the project with
over 40 contributions made by different programmers. Thus by considering Moran
processes with population size greater than 2 we are taking in to account the
effect of complex population dynamics. By considering sophisticated strategies
we are taking in to effect the reputation of a strategy during each interaction.

@@

Appendix~\ref{app:list_of_players} shows all the players in question. More
information about each player can be obtained in the documentation for
\cite{axelrodproject}. The memory depth of the used strategies is shown in
Table~\ref{tbl:memory_depth_count}.

\begin{table}[!hbtp]
    \centering
        \begin{subfigure}[t]{\textwidth}
            \centering
                \input{../tbl/memory_depth_count.tex}
                \caption{Memory depth}
                \label{tbl:memory_depth_count}
        \end{subfigure}
        \vspace{.5cm}

        \begin{subfigure}[t]{\textwidth}
            \centering
                \input{../tbl/stochastic_count.tex}
                \caption{Stochastic versus deterministic}
                \label{tbl:stochastic_count}
        \end{subfigure}
        \caption{Summary of properties of used strategies}
\end{table}

All strategies are paired and these pairs are used in 2000 repetitions of a
Moran process assuming a starting population of \((N/2, N/2)\). This is repeated
for even \(N\) between 2 and 14. The fixation probability is then estimated for
each value of \(N\).

Note that due to the high computational cost of these experiments, for any given
interaction between two players within the Moran process the outcome is sampled
from a pre computed cache of 1000 match outcomes. This is carried out using the
approximate Moran process implemented in \cite{axelrodproject}.

As an example, Figure~\ref{fig:players_with_most_scores} shows the scores
between two players that over the 1000 outcomes gives 971 different scores.

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=.4\textwidth]{../img/players_with_most_scores.pdf}
    \caption{All possible scores for the pair of strategies that have the most
    different number of match outcomes}
    \label{fig:players_with_most_scores}
\end{figure}

Section~\ref{sec:validation} will validate this approach against theoretic
results.

@@

Using this comparisons of \(x_{N/2}\) are shown in
Figure~\ref{fig:comparison_deterministic}. The points represent the simulated
values and the line shows the theoretic value. Note that these are all
deterministic strategies and show a perfect match up between the expected value
of (\ref{equ:fixation_probability}) and the actual Moran process for all
strategies pairs.

@@

Figure~\ref{fig:comparison_stochastic} shows the fixation probabilities for
stochastic strategies. These are no longer a good match which highlights the
weakness of the analytical formulae that relies on the average payoffs. A
detailed analysis of the 172 strategies considered will be shown in the next
Section.

@@

@@

Figures~\ref{fig:fixation_heatmap_invade} shows the pairwise fitness for
strategies on the columns axis invading a population of strategies on the row
axis.

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_invade.pdf}
        \caption{\((N,i)=(2, 1)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_4_invade.pdf}
        \caption{\((N,i)=(4, 1)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_6_invade.pdf}
        \caption{\((N,i)=(6, 1)\)}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_8_invade.pdf}
        \caption{\((N,i)=(8, 1)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_10_invade.pdf}
        \caption{\((N,i)=(10, 1)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_invade.pdf}
        \caption{\((N,i)=(12, 1)\)}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_invade.pdf}
        \caption{\((N,i)=(14, 1)\)}
    \end{subfigure}%
    \caption{Pairwise fixation probability \(x_{1}\) of all strategies}
    \label{fig:fixation_heatmap_invade}
\end{figure}

Figure~\ref{fig:invasion_boxplot_invade} shows the fixation probabilities for each
strategy when invading another strategy.

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_2_invade.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%

    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_4_invade.pdf}
        \caption{\(N=4\)}
    \end{subfigure}%

    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_6_invade.pdf}
        \caption{\(N=6\)}
    \end{subfigure}%

    % TODO be more selective here: just picking out the ones for which we
    % currently have data
    %\begin{subfigure}[htbp]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/boxplot_8_invade.pdf}
        %\caption{\(N=8\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/boxplot_10_invade.pdf}
        %\caption{\(N=10\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/boxplot_12_invade.pdf}
        %\caption{\(N=12\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/boxplot_14_invade.pdf}
        %\caption{\(N=14\)}
    %\end{subfigure}%
    \caption{Invasion fixation probabilities of all strategies}
    \label{fig:invasion_boxplot_std}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_coexist.pdf}
        \caption{\((N,i)=(2, 1)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_4_coexist.pdf}
        \caption{\((N,i)=(4, 2)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_6_coexist.pdf}
        \caption{\((N,i)=(6, 3)\)}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_8_coexist.pdf}
        \caption{\((N,i)=(8, 4)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_10_coexist.pdf}
        \caption{\((N,i)=(10, 5)\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_coexist.pdf}
        \caption{\((N,i)=(12, 6)\)}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_coexist.pdf}
        \caption{\((N,i)=(14, 7)\)}
    \end{subfigure}%
    \caption{Pairwise fixation probability \(x_{N/2}\) of all strategies}
    \label{fig:fixation_heatmap_coexist}
\end{figure}

Figure~\ref{fig:resistance_boxplot_resist} shows the fixation probabilities for
each strategy when resisting another strategy.
Figure~\ref{fig:coexistance_boxplot_coexist} shows the fixation probabilities for
each strategy when initially coexisting with another strategy.

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_2_resist.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%

    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_4_resist.pdf}
        \caption{\(N=4\)}
    \end{subfigure}%

    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_6_resist.pdf}
        \caption{\(N=6\)}
    \end{subfigure}%

    % TODO be more selective here: just picking out the ones for which we
    % currently have data
    %\begin{subfigure}[htbp]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/boxplot_8_resist.pdf}
        %\caption{\(N=8\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/boxplot_10_resist.pdf}
        %\caption{\(N=10\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/boxplot_12_resist.pdf}
        %\caption{\(N=12\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/boxplot_14_resist.pdf}
        %\caption{\(N=14\)}
    %\end{subfigure}%
    \caption{Resistance fixation probabilities of all strategies}
    \label{fig:resistance_boxplot_std}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_2_coexist.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/boxplot_4_coexist.pdf}
        %\caption{\(N=4\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/boxplot_6_coexist.pdf}
        %\caption{\(N=6\)}
    %\end{subfigure}%

    \begin{subfigure}[htbp]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_8_coexist.pdf}
        \caption{\(N=8\)}
    \end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/boxplot_10_coexist.pdf}
        %\caption{\(N=10\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/boxplot_12_coexist.pdf}
        %\caption{\(N=12\)}
    %\end{subfigure}%

    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_14_coexist.pdf}
        \caption{\(N=14\)}
    \end{subfigure}%
    \caption{Coexistance fixation probabilities of all strategies}
    \label{fig:coexistance_boxplot_std}
\end{figure}

Figures~\ref{fig:ranks_v_size_invade},~\ref{fig:ranks_v_size_resist}
and~\ref{fig:ranks_v_size_coexist} show the median rank of each strategy against
population size in the standard and noisy settings. Note that these ranks are
not necessarily integers as group ties are given the average rank.

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{../img/relationship_between_median_ranks_invade.pdf}
    \caption{Relationship between Median rank for population size for strategies
    invading}
    \label{fig:relationship_ranks_v_size_invasion}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{../img/relationship_between_median_ranks_resist.pdf}
    \caption{Relationship between Median rank for population size for strategies
    resisting}
    \label{fig:relationship_ranks_v_size_resistance}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{../img/relationship_between_median_ranks_coexist.pdf}
    \caption{Relationship between Median rank for population size for strategies
    coexisting}
    \label{fig:relationship_ranks_v_size_coexist}
\end{figure}

Tables~\ref{tbl:linear_coeficients_invade},~\ref{tbl:linear_coeficients_resist}
and~\ref{tbl:linear_coeficients_coexist} show the coefficients and \(R^2\) value
of the linear model relating the rank in a particular sized population to the
ranks in other populations sizes.
% TODO Discuss these tables: show that none of the models are great (R^2) BUT it
% does show that the coefficient of the N=2 column is always low whereas the
% coefficient of the N=14 column is high even in the N=4 row. So how well you do
% in  a match (N=2) has got very little to do with an evolutionary process.

\begin{table}[!hbtp]
    \centering
    \begin{subfigure}{.5\textwidth}
        \centering
        \input{"../tbl/linear_coeficients_invade.tex"}
        \caption{Linear model coefficients for ranks for invasion}
        \label{tbl:linear_coeficients_invade}
    \end{subfigure}%
    ~
    \begin{subfigure}{.5\textwidth}
        \centering
        \input{"../tbl/linear_coeficients_resist.tex"}
        \caption{Linear model coefficients for ranks for resistance}
        \label{tbl:linear_coeficients_resist}
    \end{subfigure}

    \begin{subfigure}{.5\textwidth}
        \centering
        \input{"../tbl/linear_coeficients_coexist.tex"}
        \caption{Linear model coefficients for ranks for coexistance}
        \label{tbl:linear_coeficients_coexist}
    \end{subfigure}
    \caption{Linear coefficients}
\end{table}

>>>>

Figure~\ref{fig:moran_process} shows a diagrammatic representation of the Moran
process. This process is a stochastic birth death process on a finite population
in which the population size stays constant over time. Individuals are
\textbf{selected} according to a given fitness landscape. Once selected, a given
individual is reproduced and similarly another individual is chosen to be
removed from the population. In some settings mutation is also considered but
without mutation (the case considered in this work) this process will arrive at
an absorbing state where the population is entirely made up of a single
individual. The probability with which a given strategy is the survivor is
called the fixation probability. A more detailed analytic description of this
is given in Section~\ref{sec:validation}.

@@

The Moran process was initially introduced in \cite{Moran1957} in a genetic
setting. It has since been used in a variety of settings including the
understanding of the spread of cooperative behaviour. However, as stated before,
these mainly consider non sophisticated strategies. Some work has looked at
evolutionary stability of strategies within the Prisoner's Dilemma \cite{Li2014}
but this is not done in the more widely used setting of the Moran process but in
terms of infinite population stability. In \cite{Baek2016} Moran processes are
looked at in a theoretic framework for a small subset of strategies. In
\cite{Lee2015} machine learning techniques are used to train a strategy capable
of resisting invasion and also invade any memory one strategy. Recent work
\cite{Hilbe2017} has investigated the effect of memory length on strategy
performance and the emergence of cooperation but this is not done in Moran
process context and only considers specific cases of memory 2 strategies.
% TODO Is this OK? We should add more.

The contribution of this work is a detailed and extensive analysis of absorption
probabilities for 172 strategies. These strategies and the numerical simulations
are from~\cite{axelrodproject} which is an open source research library written
for the study of the IPD\@. The strategies and simulation frameworks are
automatically tested in accordance to best research software practice. The large
number of strategies are available thanks to the open source nature of the
project with over 40 contributions made by different programmers. Thus by
considering Moran processes with population size greater than 2 we are taking in
to account the effect of complex population dynamics. By considering
sophisticated strategies we are taking in to effect the reputation of a strategy
during each interaction.

@@

Appendix~\ref{app:list_of_players} shows all the players in question. More
information about each player can be obtained in the documentation for
\cite{axelrodproject}. There are \input{../tbl/num_stochastic.tex}stochastic and
\input{../tbl/num_deterministic.tex}deterministic strategies. Their memory
depth is shown in Table~\ref{tbl:memory_depth_count}.

\begin{table}[!hbtp]
    \centering
        \input{../tbl/memory_depth_count.tex}
        \caption{Memory depth}
        \label{tbl:memory_depth_count}
\end{table}

All strategies are paired and these pairs are used in 1000 repetitions of a
Moran process assuming a starting population of \((N/2, N/2)\). This is repeated
for even \(N\) between 2 and 14. The fixation probability is then estimated for
each value of \(N\).
% TODO The above is no longer true.

Note that due to the high computational cost of these experiments, for any given
interaction between two players within the Moran process the outcome is sampled
from a pre computed cache of 1000 match outcomes. This is carried out using an
software written for the purpose of this work. This has been
implemented in \cite{axelrodproject} ensuring that it can be used to either
reproduce the work or carry out further work.

Figure~\ref{fig:number_of_stochastic_match_outcomes} shows the distribution of
the number of outcomes between all strategy pairs.
Tables~\ref{tbl:number_of_stochastic_match_outcomes} shows that 95\% of the
stochastic matches have less than 786 unique outcomes whilst the maximum number
is 971. This ensures that using a set of cached results from 1000 precomputed
matches is sufficient for the analysis taking place here.

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{../img/number_of_match_outcomes.pdf}
        \caption{All matches}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{../img/number_of_stochastic_match_outcomes.pdf}
        \caption{Stochastic matches}
    \end{subfigure}%
    \caption{The distribution of the number of unique outcomes used as the
    cached results}
    \label{fig:number_of_stochastic_match_outcomes}
\end{figure}

\begin{table}[!hbtp]
    \centering
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \input{../tbl/number_of_match_outcomes.tex}
        \caption{All matches}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \input{../tbl/number_of_stochastic_match_outcomes.tex}
        \caption{Stochastic matches}
    \end{subfigure}%
    \caption{Summary statistics for the number of different match outcomes used
    as the cached results}
    \label{tbl:number_of_stochastic_match_outcomes}
\end{table}

Section~\ref{sec:validation} will validate the methodology used here against
known theoretic results.

@@

Using this comparisons of \(x_1, x_{N/2}, x_{N-1}\) are shown in
Figure~\ref{fig:comparison_deterministic}. The points represent the simulated
values and the line shows the theoretic value. Note that these are all
deterministic strategies and show a perfect match up between the expected value
of (\ref{equ:fixation_probability}) and the actual Moran process for all
strategies pairs.

@@

Figure~\ref{fig:comparison_stochastic} shows the fixation probabilities for
stochastic strategies. These are no longer a good match which highlights the
weakness of the analytical formulae that relies on the average payoffs. A
detailed analysis of the 172 strategies considered, using direct Moran processes
will be shown in the next Section.

@@

This section will outline the data analysis carried out:

\begin{itemize}
    \item Section~\ref{sec:two_individuals} will consider the specific case of
        \(N=2\).
    \item Section~\ref{sec:strong_invaders} will investigate the effect of
        population size on the ability of a strategy to invade another
        population. This will highlight how complex strategies with long
        memories outperform simpler strategies.
    \item Section~\ref{sec:strong_resistors} will similarly investigate the
        ability to defend against an invasion.
    \item Section~\ref{sec:population_size} will investigate the relationship
        between performance for differing population sizes. This highlights the
        importance of considering population dynamics over large populations.
    \item Section~\ref{sec:fitness} will calculate the relative fitness of all
        strategies.
\end{itemize}

\subsection{The special case of \(N=2\)}\label{sec:two_individuals}

% TODO Move the case 2 graphics to here.

@@

In this section \(x_i\) will be investigated: the probability of 1 individual of
a given type successfully becoming fixated in a population of \(N - 1\) other
individuals. Figures~\ref{fig:fixation_heatmap_invade} shows these values for
the players along the vertical axis when matched against the players on the
horizontal axis. It can be seen that invasion is in general more challenging for
\(N=7\) and \(N=11\) in comparison to \(N=2\).
%TODO Change this to N=14
This information is summarised in Figure~\ref{fig:fixation_boxplot_invade}
showing the median fixation as well as the neutral fixation for each given
scenario.

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_invade.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_7_invade.pdf}
        \caption{\(N=7\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_11_invade.pdf}
        \caption{\(N=11\)}

    %TODO Replace N=11 with N=14
    \end{subfigure}%

    \caption{Pairwise fixation probability \(x_{1}\) of all strategies}
    \label{fig:fixation_heatmap_invade}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_2_invade.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_7_invade.pdf}
        \caption{\(N=7\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_11_invade.pdf}
        \caption{\(N=11\)}
    \end{subfigure}%

    % TODO Replace N=11 with N=14 (when we have more data).
    \caption{Median probabilities \(x_{1}\) of all strategies as well as the
    neutral fixation probability}
    \label{fig:fixation_boxplot_invade}
\end{figure}

For \(N\in\{2, 7, 11\}\) the top five strategies are given in
% TODO Change N=11 to N=14
Tables~\ref{tbl:top_five_invade}. It can be seen that for \(N=2\), as described
in~\cite{Press2012}, zero determinant strategies perform well. There is a
single strategy with infinite memory in the top five but this is in fact a meta
strategy that plays with a team of memory one strategies picking out the top
performer at each stage. The remaining strategy ``Feld" is the corresponding
strategy submitted to the first tournament by Axelrod~\cite{Axelrod1980a}. All
these strategies are stochastic.

\begin{table}[!hbtp]
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_2_invade.tex}
        \caption{\(N=2\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_7_invade.tex}
        \caption{\(N=7\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_11_invade.tex}
        \caption{\(N=11\)}
    \end{subfigure}
    %TODO Change N=11 to N=14
    \caption{Properties of top five invaders}
    \label{tbl:top_five_invade}
\end{table}

% TODO Write a little conclusion about invaders and introduce next section.

\subsection{Strong resistors}\label{sec:strong_resistors}

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_invade.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_7_resist.pdf}
        \caption{\(N=7\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_11_resist.pdf}
        \caption{\(N=11\)}

    %TODO Replace N=11 with N=14
    \end{subfigure}%

    \caption{Pairwise fixation probability \(x_{N-1}\) of all strategies}
    \label{fig:fixation_heatmap_resist}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_2_invade.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_7_resist.pdf}
        \caption{\(N=7\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_11_resist.pdf}
        \caption{\(N=11\)}
    \end{subfigure}%

    % TODO Replace N=11 with N=14 (when we have more data).
    \caption{Median probabilities \(x_{N-1}\) of all strategies as well as the
    neutral fixation probability}
    \label{fig:fixation_boxplot_resist}
\end{figure}

\begin{table}[!hbtp]
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_7_resist.tex}
        \caption{\(N=7\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_11_resist.tex}
        \caption{\(N=11\)}
    \end{subfigure}
    %TODO Change N=11 to N=14
    \caption{Properties of top five strategies resistors}
    \label{tbl:top_five_invade}
\end{table}

\subsection{The effect of population size}\label{sec:population_size}

Figures~\ref{fig:ranks_v_size_invade},~\ref{fig:ranks_v_size_resist}
and~\ref{fig:ranks_v_size_coexist} show the median rank of each strategy against
population size. Note that these ranks are
not necessarily integers as group ties are given the average rank.

@@

Tables~\ref{tbl:correlation_coeficients_invade},~\ref{tbl:correlation_coeficients_resist}
and~\ref{tbl:correlation_coeficients_coexist} show the correlation coefficients
of the ranks in of strategies in differing population size. This is shown
graphically in Figure~\ref{fig:correlation_coefficients}. It is immediate to
note that how well a strategy performs in any Moran process for \(N>2\) has
little to do with the performance for \(N=2\).
% TODO This is a really good conclusion I think: it shows that when studying
% population dynamics it is important to consider larger populations.

\begin{table}[!hbtp]
    \centering
    \begin{subfigure}{\textwidth}
        \centering
        \input{"../tbl/correlation_coeficients_invade.tex"}
        \caption{Correlation coefficients for ranks for invasion}
        \label{tbl:correlation_coeficients_invade}
    \end{subfigure}%

    \begin{subfigure}{\textwidth}
        \centering
        \input{"../tbl/correlation_coeficients_resist.tex"}
        \caption{Correlation coefficients for ranks for resistance}
        \label{tbl:correlation_coeficients_resist}
    \end{subfigure}

    \begin{subfigure}{\textwidth}
        \centering
        \input{"../tbl/correlation_coeficients_coexist.tex"}
        \caption{Correlation coefficients for ranks for coexistance}
        \label{tbl:correlation_coeficients_coexist}
    \end{subfigure}
    \caption{Correlation coefficients}
\end{table}

\begin{figure}[!htbp]
	\centering
	\begin{subfigure}[t]{.3\textwidth}
		\centering
		\includegraphics[width=.9\textwidth]{../img/correlation_heatmap_invade.pdf}
		\caption{Rank based on \(x_1\)}
    \end{subfigure}
    ~
	\begin{subfigure}[t]{.3\textwidth}
		\centering
		\includegraphics[width=.9\textwidth]{../img/correlation_heatmap_resist.pdf}
        \caption{Rank based on \(x_{N - 1}\)}
    \end{subfigure}
    ~
	\begin{subfigure}[t]{.3\textwidth}
		\centering
		\includegraphics[width=.9\textwidth]{../img/correlation_heatmap_coexist.pdf}
        \caption{Rank based on \(x_{N/2}\)}
    \end{subfigure}
    \caption{Correlation coefficients for ranks}
    \label{fig:correlation_coefficients}
\end{figure}
